Data 621---HW1---Regression Model---Version 2

### 2020-09-09 HW1/RegModel_Adler.Rmd
Finish test set. Up to predictions.

# Left join MBtrnlng to BCL. 
MBtrnlng <- BCL[MBtrnlng]

@@

The stepwise model has the best \(R^2\) of the three and the best AIC. Using
accepted rules of thumb, a difference of more than 10 indicates no support for
the model with the higher AIC. The magnitude is irrelevant; it is a function of
the number of observations. The difference between the AIC of the saturated
model and the step model is
`r prettyNum(AIC(saturatedModel) - AIC(stepModel), digits = 2L)`. This shows
that the saturated model, and obviously the null model, should be completely
ignored in favor of the stepwise model with pairwise within class interactions.

Most of the coefficients are reasonable within the context of the game of
baseball. These two statements are axiomatic:

@@

### Criteria
As a devout follower of Burnham & Anderson (2002), I prefer to use AIC whenever
possible. This includes inherent recognition of parsimony. As discussed in the
previous section, for an AIC difference of 10 or greater, the model with the
higher AIC has effectively no support. The stepwise model with within-class
pairwise interactions had the lowest AIC by hundreds.

@@

### Model Evaluations
In the table below are the RMSE, \(R^2\), and significance of the F-statistic
for each of the three models as applied to the **testing** set.

```{r buildTests}
MBtstlng <- BCL[MBtstlng]
MBtstlng[!is.na(Lambda), Value := BxCox(Value, Lambda)]
MBtstlng[, Lambda := NULL]
MBtstlngSC <- copy(MBtstlng)

@@

# Center and Scale
MBtstlngSC[, Value := replace(Value, is.na(Value), mean(Value, na.rm = TRUE)),
       keyby = Metric]
MBtstlngUnscale <- MBtstlngSC[, .(Mean = mean(Value), SD = sd(Value)),
                          keyby = Metric]
MBtstlngSC[, Value := scale(Value, center = TRUE, scale = TRUE), keyby = Metric]
MBtstSC <- dcast(MBtstlngSC, INDEX ~ Metric, value.var = 'Value')
MBtstSC[, TARGET_WINS := TARGET_WINS * 
          MBtstlngUnscale[Metric == 'TARGET_WINS', SD] +
          MBtstlngUnscale[Metric == 'TARGET_WINS', Mean]]
```

@@

```{r loadPackages, echo=TRUE, eval=FALSE}
```
```{r readData, echo=TRUE, eval=FALSE}
```
```{r missingTable, echo=TRUE, eval=FALSE}
```
```{r summaryTable, echo=TRUE, eval=FALSE}
```
```{r boxPlot1, echo=TRUE, eval=FALSE}
```
```{r boxPlot2, echo=TRUE, eval=FALSE}
```
```{r corrgram, echo=TRUE, eval=FALSE}
```
```{r imputeMean, echo=TRUE, eval=FALSE}
```
```{r centerScale, echo=TRUE, eval=FALSE}
```
```{r plotScaled, echo=TRUE, eval=FALSE}
```
```{r boxCox, echo=TRUE, eval=FALSE}
```
```{r reScale, echo=TRUE, eval=FALSE}
```
```{r reImputeThenScale, echo=TRUE, eval=FALSE}
```
```{r lm, echo=TRUE, eval=FALSE}
```
```{r nullOutput, echo=TRUE, eval=FALSE}
```
```{r satOutput, echo=TRUE, eval=FALSE}
```
```{r stepOutput, echo=TRUE, eval=FALSE}
```

>>>>

# Left join MBtrnlng to BCL. 
MBtrnlng <- BCL[MBtrnlng, on = 'Metric']

@@

#### Statistics
The stepwise model has the best \(R^2\), adjusted  \(R^2\), and AIC of the three
models. Using accepted rules of thumb, a difference of more than 10 indicates no
support for the model with the higher AIC. The magnitude is irrelevant; it is a
function of the number of observations. The difference between the AIC of the
saturated model and the step model is
`r prettyNum(AIC(saturatedModel) - AIC(stepModel), digits = 2L)`. This shows
that the saturated model, and obviously the null model, should be completely
ignored in favor of the stepwise model with pairwise within class interactions.

#### Residual Plots
```{r residPlots, fig.width=7}
par(mfrow = c(2, 2))
plot(saturatedModel$fitted.values, studres(saturatedModel),
     main = 'Saturated Model', xlab = 'Predicted Values',
     ylab = 'Studentized Residuals', xlim = c(0, 160), ylim = c(-6, 6))
plot(stepModel$fitted.values, studres(stepModel),
     main = 'Stepwise Pairwise Model', xlab = 'Predicted Values',
     ylab = 'Studentized Residuals', xlim = c(0, 160), ylim = c(-6, 6))
plot(nullModel$fitted.values, studres(nullModel),
     main = 'Null Model', xlab = 'Predicted Values',
     ylab = 'Studentized Residuals', xlim = c(0, 160), ylim = c(-6, 6))
par(mfrow = c(1, 1))
```

Both the saturated and the stepwise models look to have a basically normal
distribution of their residuals. The null model returns a single value,
explaining the bizarness of the graph.

The **actual** model to be used for the prediction will be the model which
returns the best RMSE and MAPE on the test set.

#### Explanation of Selected Model
Most of the coefficients are reasonable within the context of the game of
baseball. These two statements are axiomatic:

@@

### Criteria
As a devout follower of Burnham & Anderson (2002), I prefer to use AIC whenever
possible. This includes inherent recognition of parsimony. As discussed in the
previous section, for an AIC difference of 10 or greater, the model with the
higher AIC has effectively no support. The stepwise model with within-class
pairwise interactions had the lowest AIC by hundreds. The various statistics and
plots requested for the training data are also in the previous section.

@@

### Model Evaluations
In the table below are the RMSE and MAPE of each of the three models developed
above when applied to the **testing** set.

```{r buildTestSet}
MBtstlng <- BCL[MBtstlng, on = 'Metric']
MBtstlng[!is.na(Lambda), Value := BxCox(Value, Lambda)]
MBtstlng[, Lambda := NULL]
MBtstlngSC <- copy(MBtstlng)

@@

# Center and Scale
MBtstlngSC[, Value := replace(Value, is.na(Value), mean(Value, na.rm = TRUE)),
       keyby = Metric]
MBtstlngUnscale <- MBtstlngSC[, .(Mean = mean(Value), SD = sd(Value)),
                          keyby = Metric]
MBtstlngSC[, Value := scale(Value, center = TRUE, scale = TRUE), keyby = Metric]
MBtstSC <- dcast(MBtstlngSC, INDEX ~ Metric, value.var = 'Value')
MBtstSC[, TARGET_WINS := TARGET_WINS * 
          MBtstlngUnscale[Metric == 'TARGET_WINS', SD] +
          MBtstlngUnscale[Metric == 'TARGET_WINS', Mean]]
nmP <- predict(nullModel, MBtstSC)
smP <- predict(saturatedModel, MBtstSC)
stmP <- predict(stepModel, MBtstSC)
nmRMSE <- sqrt(mean((MBtstSC$TARGET_WINS - nmP) ^ 2))
nmMAPE <- mean(abs((MBtstSC$TARGET_WINS - nmP) / MBtstSC$TARGET_WINS))
smRMSE <- sqrt(mean((MBtstSC$TARGET_WINS - smP) ^ 2))
smMAPE <- mean(abs((MBtstSC$TARGET_WINS - smP) / MBtstSC$TARGET_WINS))
stmRMSE <- sqrt(mean((MBtstSC$TARGET_WINS - stmP) ^ 2))
stmMAPE <- mean(abs((MBtstSC$TARGET_WINS - stmP) / MBtstSC$TARGET_WINS))
knitr::kable(data.frame(Model = c("Null", "Saturated", "Stepwise Pairwise"),
                        RMSE = c(nmRMSE, smRMSE, stmRMSE),
                        MAPE = c(nmMAPE, smMAPE, stmMAPE)),
             digits = 3L, caption = 'Test Set Results')
```

The stepwise model allowing for pairwise interactions is the winner in both
cases, as was expected.

### Predictions
We will use the stepwise-pairwise model to predict `TARGET_WINS` for the
separately provided evaluation set.

@@

```{r loadPackages, echo=TRUE, eval=FALSE}
```
```{r readData, echo=TRUE, eval=FALSE}
```
```{r missingTable, echo=TRUE, eval=FALSE}
```
```{r summaryTable, echo=TRUE, eval=FALSE}
```
```{r boxPlot1, echo=TRUE, eval=FALSE}
```
```{r boxPlot2, echo=TRUE, eval=FALSE}
```
```{r corrgram, echo=TRUE, eval=FALSE}
```
```{r testTrain, echo=TRUE, eval=FALSE}
```
```{r imputeMean, echo=TRUE, eval=FALSE}
```
```{r centerScale, echo=TRUE, eval=FALSE}
```
```{r plotScaled, echo=TRUE, eval=FALSE}
```
```{r boxCox, echo=TRUE, eval=FALSE}
```
```{r reScale, echo=TRUE, eval=FALSE}
```
```{r reImputeThenScale, echo=TRUE, eval=FALSE}
```
```{r lm, echo=TRUE, eval=FALSE}
```
```{r nullOutput, echo=TRUE, eval=FALSE}
```
```{r satOutput, echo=TRUE, eval=FALSE}
```
```{r stepOutput, echo=TRUE, eval=FALSE}
```
```{r residPlots, echo=TRUE, eval=FALSE}
```
```{r buildTestSet, echo=TRUE, eval=FALSE}
```
